%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Simon}{Thornewill von Essen}
\position{Data Scientist}
\address{Bonn area, Germany}

\mobile{[mobile]}
\email{[email]}
\homepage{datasciencedemonstrated.com}
\github{sthornewillve}
\linkedin{sthornewillve}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world. Now!"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {}
  {company \\address and street no.\\city, area code}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{RE: Job Application for \href{}{}} % Add URL in first brackets and position in the next
% How the letter is opened
\letteropening{Dear [Recipient],}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae, Reference}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Simon Thornewill von Essen~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  \lettersection{About Me}
  As a data scientist, my mission is to solve business problems by using machine
  learning techniques and communicating the methods/results clearly to technical
  and non-technical stakeholders. I am committed to life-long learning and
  curiosity to continue my growth in a constantly shifting field.

  \lettersection{Why am I applying at [Company] and how can I help?}
  I would be overjoyed to work at [Company] because I am actively seeking out
  experienced data scientists to collaborate and expand my knowledge with. I am
  also very interested in work environments that promote collaboration and
  gaining varied experience in different industries. Exposure to a range of
  business problems will lead me to grow substantially as a data scientist,
  which is why I am applying for this position.

  During my nanodegree with Udacity, I did a project where I performed an
  AB-test on e-commerse data using python. I simulated the predicted outcome
  under a null-hypothesis and compared the difference between the real data and
  calculated the probability of this outcome (p-value). I compared these with a
  logistic regression and found that both of these models predicted that the
  change was likely the result of random chance. If this project had been done
  in a business setting then this would have the potential to prevent a poor
  design choice being made to the company website.

  During my internship at DPDHL, I wrote an Invoice/Order matching algorithm
  with python. Challenges accompanying this project was finding keywords and
  associations between words and ranked the best possible matches so that a
  human could quickly choose the correct decision. The algorithm is currently in
  production and makes the matching process more efficient. This shows that I am
  not only able to tackle large problems but I am also able to implement and
  explain the use of these tools so they can be used in my absence.

  \lettersection{Conclusion}
  In short, I believe I would make an excellent candidate for this position
  because I have experience in tackling complex problems using the tools that
  would be required for this position. I have practical experience analyzing
  data using machine learning in both Python and R and presenting these findings
  to others.

  Thank you for reading my application and considering me for the position or
  any other position you think would be suitable. I currently have flexible
  availability for interview scheduling and genuinely look forward to future
  communication. I can be reached via the contact information or situated in the
  header email anytime. LinkedIn or email works best to arrange a call. I wish
  you and your co-workers at [Company] the best in your endeavours for the future.


\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
