%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}
    \cventry
      {Udacity} % Institution
      {Data Analysis Nanodegree} % Degree
      {udacity.com} % Location
      {Oct. 2017 - Exp. Feb. 2018} % Date(s)
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Used \textbf{Python} and \textbf{R} to import data, perform calculations using industry standard packages. (Python: Matplotlib, Pandas, Numpy. R: Dplyr, Ggplot2)}
          \item {Analyzed \textbf{real-world data sets}, required substantial \textbf{data wrangling}.}
          \item {Learned how to write \textbf{SQL} queries including \textbf{joins, subqueries and aggregation}.}
          \item {Created visualisations for data story-telling using \textbf{Tableau.}}
          %\item {Learned Statistics and carried out A-B tests.}
        \end{cvitems}
      }

      \cventry
      {Udemy}
      {Machine Learning A-Z} % Degree
      {udemy.com} % Location
      {Sep. 2017 - Oct 2017} % Dates
      {
        \begin{cvitems} % Description(s) bullet points
          \item {Learned how to use \textbf{machine learning} to model, predict and classify data (Regression, Classification, Clustering, Dimensionality Reduction, Deep Learning, etc.)}
          \item {Learned how to use these algorithms in \textbf{both R} and \textbf{Python} (R: caret, h2o. Python: sklearn, scipy, tensorflow, keras)}
          \item {Used these techniques on data and assessed their performance using \textbf{cross-validation} and \textbf{confusion matrices}.}
        \end{cvitems}
      }

  \cventry
    {The University of Edinburgh} % Institution
    {Master of Chemistry (M. Chem)} % Degree
    {Edinburgh, Scotland} % Location
    {Sep. 2012 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Researched the sustainable activaton of Boronic Esters, involved \textbf{designing experiments and hypotheses} and \textbf{drawing conclusions} from results.}
        \item {Used \textbf{statistics} to calculate and propogate errors.}
        \item {Presented findings of research in various \textbf{presentations to groups of 5 to 150 people.}}
        \item {Reviewed literature to \textbf{quickly understand the state of the art} on various topics and find gaps to for futher investigation.}
      \end{cvitems}
    }

    \cventry
    {The Knowledge Academy} %Degree
    {PRINCE2 Foundation} % Location
    {Edinburgh, United Kingdom} % Location
    {Apr. 2016 - Apr. 2016} % Dates
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Gained an understanding of project management to \textbf{plan the delivery business products according to an agreed business case.}}
  %      \item {Lorem ipsum dolor sit amet, consectetuer adipiscing elit.}
  %      \item {Topics included asses}
      \end{cvitems}
    }

\end{cventries}

\begin{comment}
  \cventry
    {Bonn International School} % Institution
    {International Baccalaureate (IB)} % Degree
    {Bonn, Germany} % Location
    {Sep. 2010 - May. 2012} % Date(s)
    {
      \begin{cvitems} %Description(s) bullet points
        \item {Took part in "Theory of Knowledge", learned to think critically.}
        \item {Learned time managment skills used for studying a broad change of subjects.
        \item {Conducted individual research experiment in Chemistry which resulted in an "extended essay".}
        \item {Immersed in a diverse culture.}
      \end{cvitems}
    }
\end{comment}

%---------------------------------------------------------
