%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Edinburgh University Salsa Soceity} % Organization/group
    {Lead Treasurer} % Affiliation/role
    {Edinburgh} % Location
    {May. 2016 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Trusted with the responsibility of the society's finances.}
        \item {Position required consistent time managment and organisation skills in order to keep the ledger updated and accurate.}
        \item {Advised society's president and committee on financial decisions.}
        \item {Overhauled the documentation system from "pen and paper" to a digital system using Google Docs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {School of Chemistry} % Organization/group
    {Student Representative} % Affiliation/role
    {Edinburgh} % Location
    {Sep. 2014 - May. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Communicated feedback from students to the faculty regarding “Environmental Chemistry 2” and “Chemistry 3” courses.}
        \item {Practiced distilling information to find the most urgent and important information to relay at meetings.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Edinburgh University Students' Association} % Organization/group
    {Welcome Week Volunteer} % Affiliation/role
    {Edinburgh} % Location
    {Sep. 2013 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Managed queues, answered questions and gave directions to new students.}
        \item {Required a friendly approachable demeanor in addition to quickly understanding and meeting the needs of each approaching student.}
        \item {Trained in observation skills to help notice if a student was too shy to ask for help or was clearly in need of assistance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bonn International School} % Organization/group
    {Fundraiser Organiser} % Affiliation/role
    {Bonn} % Location
    {Sep. 2011 - May. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organised quiz-night fundraiser where approximately €1,500 was raised for an orphanage in Kenya.}
        \item {Developed leadership skills by coordinating many students and assigning tasks according to their individual capabilities.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
