%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Udacity} % Institution
    {\href{https://github.com/SThornewillvE/Udacity-Project---Exploring-Wine-Data}{White Wine Dataset Analysis using R, }} % Project Title
    {} % Location
    {Dec. 2017 - Jan. 2018} % Date
    {
    \begin{cvitems} % Description(s) bullet points
      \item {Analysed the chemical components of white wine to predict quality.}
      \item {Carried out univariate, bivariate and multivariate analyses in ggplot2.}
      \item {Discussed which variables were or were not correlated with quality.}
    \end{cvitems}
    }

  \cventry
    {Udacity} % Institution
    {\href{https://github.com/SThornewillvE/Udacity-Project---AB-testing}{AB-Testing using Python, }} % Project Title
    {} % Location
    {Nov. 2017} % Date
    {
    \begin{cvitems} % Description(s) bullet points
      \item {Tested whether a change in website layout created a statistically significant improvement.}
      \item {Compared resulting p-value with that derived from a logistic regression.}
      \item {Found that the change was not statistically significant in either case and was independent of country.}
    \end{cvitems}
    }

  \cventry
    {The University of Edinburgh} % Institution
    {\href{https://www.evernote.com/shard/s234/sh/559f3e12-1aa6-4d68-a68b-3ddaf8526b9c/ccfcc1f7a32c8966587de6b8983877cb}{MChem Research Project, }} % Project Title
    {} % Location
    {Oct. 2016 - Mar. 2017} % Date
    {
    \begin{cvitems} % Description(s) bullet points
      \item {Researched the sustainable activation of Boronic Esters, designed experiments, made hypotheses and drew conclusions from results.}
      \item {Reviewed literature to quickly understand cutting-edge research on various topics and suggested areas for further investigation}
      \item {Gave various presentations including but not limited to results to groups ranging from 5 to 150 people}
    \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
